EpisoPass: Password Management based on Episodic Memories

### 2016-12-11 paper/Password2016/junk.tex
...

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{marginnote}

@@

\usepackage{url}
% \urldef{\mailsa}\path|masui@pitecan.com|
\urldef{\mailsa}\path|***@***.***.***|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% a short form should be given in case it is too long for the running head
\titlerunning{EpisoPass: Password Management based on Episodic Memories}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
% \author{Toshiyuki Masui%
\author{***** ****
% \thanks{Thanks...}%
}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
%\institute{Faculty of Environment and Information Studies, Keio University\\
%5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
%\mailsa\\
%\url{http://pitecan.com/}}
\institute{******* ******* ******* *******\\
******, ****** *******, *******\\
\mailsa\\
% \url{http://pitecan.com/}}
\url{http://*****.***.***/}}

@@

Passwords have been used as a means of authenticating to Web services and applications
for a long time, and remain the most popular authentication method on the Internet.
%
Since short passwords are easily guessable by attackers and
using the same password for multiple services is unsafe,
a different long password should be used for each service a person uses.
However, remembering numerous long passwords is almost impossible for ordinary humans.
%
According to research conducted by Flor\^{e}ncio {\it et al.\/} in 2007,
people use on average only 6.5 different passwords to access 25 Web services, and
4.28\% of users forget their passwords within 3 months \cite{Florencio:2007:LSW:1242572.1242661}.

Since passwords are difficult to handle, various other authentication methods have been proposed.
For example, image-based authentication \cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}, 
biometrics\footnote{
  % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
  \url{https://en.wikipedia.org/w/index.php?title=Biometrics&oldid=736189000}
},
behavior-based authentication \cite{Dandapat:2015:AYD:2702123.2702457}, and many others.

@@

\marginnote{I'd hesitate to call passwords the {\it strongest\/} method. Perhaps {\it most widely deployed\/} would be less contreversial?}
However, password-based authentication is still the most
convenient and widely deployed method \cite{Bonneau:ReplacePasswords},
and is not expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.

Given we will have to continue to live with password-based authentication systems for the foreseeable future,
we have to devise practical methods for handling many passwords, and various ``password managers'' have been proposed
\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}.
%
Password managers remember users' passwords and aim to directly enter them into the login pages of the various services a user wants to access.
%
The burden on the user is reduced by requiring just a single ``master password'' to access the database of stored passwords.
%
Although password managers are widely used and a clear step forward from having to remember multiple passwords, uses nonetheless have to remember the master password or use a special hardware device for safely handling the password database, and password managers usually run on only a limited set of devices.

@@

If we want to avoid having to carry any special device for authentication,
all the information required for the authentication should be
kept in the users' brain.
%
However, the biggest problem of brain-based authentication is that
users cannot safely keep memories like long passwords or master password.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on users' episodic memories that they can never forget.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We propose a password manager \textit{EpisoPass} that generates strong passwords
based only on the user's secret episodic memories that the user cannot forget.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
% Memories in human brain are not uniform.
We keep various memories in our brain, but different memories have different natures.
Some memories are very short-lived, and others remain for a long time.
When we have a very impressive experience,
that memory will stay in the brain for a long time and
cannot easily disappear.
On the other hand, when we study math and try to remember a new formula,
it is usually hard to memorize it unless we practice a lot,
since the knowledge about the formula is not related to
any personal experiences.
The former type of memory is called the episodic memory and
people cannot easily lose it.
Memories of passwords belong to the latter type and
people cannot easily remember them, just like people cannot
remember math formulas easily.

@@

The idea of using episodic memories for authentication has a long history.
Early papers suggested using episodic memories for creating passwords.
Authentication by using secret questions,
sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
has long been used as an
alternative to password-based authentication systems.
%
% However, conversion from episodic memories to password strings
% was not studied at all.

@@

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a
candidate password string based on the selections.
When the user selects the correct answers to all the questions,
the right password is calculated and shown at the top.

@@

Questions and answers can be edited directly on the browser, and they can be
saved on the server by clicking the ``save to server'' button.
The Q-A data sets are saved on the server,
but no information about the correct answer or the
generated password is saved on the server.
The Q-A data in JSON format can be downloaded to the local machine
by clicking the ``save to file'' button.
the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.

@@

Character substitution is performed based on the hash value
calculated from concatenating all the questions and selected answers.
%
For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
to the question ``\textbf{\texttt{Who's the bully?}}'',
a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
is used for calculating the hash value.

@@

If a user doesn't like to use the EpisoPass service on the Net,
he can use an EpisoPass application on Android
which does not use network connections.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
by clicking the ``Android app'' button at the top.
The application contains all the information required for generating passwords.
(The application is compiled and built on the server.)

@@

The calculation is performed on Android without network connection,
and the user can safely generate passwords 
without feeling the fear of being observed by attackers.

\subsection{Using the browser extension}
\label{extensionsection}

@@

A browser extension is a JavaScript add-on program which runs
on top of existing Web pages.
%
Figure \ref{extension} shows the login page of Amazon.com, with which
EpisoPass questions are automatically displayed by the browser extension.
%
Here, when the Amazon login page is accessed from the browser,
the browser extension program automatically runs on the page,
acquires questions and answers from the EpisoPass server,
and shows them to the user just the same way as the Android application.
%
After answering all the questions, a password is calculated from the
selected answers and pasted to the password field of the page.
Using the extension, users can login to various services just by
answering questions, without seeing any password string.
It looks as if these services are offering
EpisoPass-based authentication.

@@

In the previous examples showing the author's EpisoPass questions,
a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.
Such strings are used because they are easily memorable.
Of course any seed string can be used as seeds for various services,
and automatic generation of seed strings is possible.

% although generating service-specific unique seed string is not trivial.
% For example, users can use the same username and password both
% for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.

@@

It is difficult to provide enough number of fake answers to a question like
``what was your favorite sport?''
because the number of possible answers are limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is easy.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', etc.
because we can use the list of states in the U.S.

In this way, fake answers can be easily generated
if it is possible to collect words which belong to the same
category as the right answer.
%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval tasks%
\cite{Huang:2012:LFC:2426725.2426728}% 
\cite{BooWa}% Boo!Wa!
\cite{Wang:2007:LSE:1441428.1442086}.
Using such systems, we can get a list of fake answers almost automatically.

@@

Although everyone has to use authentication systems on the Internet these days,
not all the people are good at handling passwords.
Even experienced computer users have trouble with passwords,
since choosing a good password is not intuitive and
people forget passwords very easily.
%
Using EpisoPass, people can use password-based systems without knowing
techniques for creating and remembering strong passwords.
They only have to provide
questions and answers based on secret episodic memories.
%
By integrating EpisoPass into existing password-based services,
people can even use services without noticing that passwords are
required for the service.
%
Our experience of using browser extensions suggests that
this approach is worth consideration.

@@

On many services, users are requested to change passwords periodically
to strengthen security.
%
Such a practice is not recommended these days
because humans cannot create strong passwords frequently\cite{Schneier:change}.
%
% A user can generate a new strong password by using a random character generator
% on a password manager, but he might want to old passwords in case some trouble happens.
%
Using EpisoPass, users can just provide a date-related question
like the last question shown in Figure \ref{web1},
and generate different strong passwords based on the answer.
Using this technique, people can easily manage old and new passwords.

% \subsection{Comparison with challenge-response authentication}
% 
% % 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
% % {\PW}を忘れたときのために、
% % あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
% % 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
% % 質問に対してユーザが答を登録するようになっている。
% % このような問題は他人が調べたり推測したりすることが容易であるうえに
% % {\SQ}の数は一般的に少なく、
% % {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘
% 
% In many services, users are advised to define answers to secret questions like
% ``what is your mother's maiden name''
% so that he can log into the service even when he forgets the password.
% This kind of authentication is far less secure than simple password systems,
% since it is fairly easy for attackers to know the right answer.
% The variation of system-provided questions are usually small, and
% such challenge-response systems are considered to be
% insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.
% 
% It would be better if the user can register his own secret questions
% based on his episodic memory.
% However, answers to user-generated challenge questions are more easily
% forgotten or cracked,
% and using simple challenge-responce is not considered to be safe enough
% \cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
% %
% Also, in this case,
% the user should register the answer to the system in addition to the question.
% Telling secret facts to service providers is like
% registering raw password string on the server,
% and it is not safe unless the strings are properly hashed and salted on the server.

@@

To prevent such trouble, it is safer to keep all the questions and answers
in a secret place or
use sufficient number of questions so that brute-force does not work.

@@

Old pictures can be used as the questions of EpisoPass,
just like the question shown at the bottom of Figure \ref{web1}.
Even when people cannot create good secret questions,
people can fairly easily select a secret image from their photo collections
and use it as the question.
For example, if you have an old picture of your friend,
you can use it as the question
and use his real name as well as other similar fake names.

@@

As shown in previous sections,
there have been many attempts for replacing password-based authentication systems,
but none of them are found to be better than
password-based systems\cite{Bonneau:ReplacePasswords}.
%
Although cognitive password systems have been studied for a
long time\cite{Lazar2011}\cite{Zviran:1990:UAC:100512.100538},
they were implemented as a replacement to password-based systems,
and no password-generation system have been proposed
based on cognitive authentication.

@@

The idea of using episodic memories for authentication is not new.
In fact, using episodic memories for selecting password
has generally been recommended,
and many current computer users are probably using password that are
in some way related to their episodic memories.

Recently, people are trying to use mobile devices for authentication,
because mobile devices remember all the user's behaviors and
the user can easily recall what he did%
\cite{Dandapat:2015:AYD:2702123.2702457}%
\cite{Das:2013:ECE:2493432.2493453}%
\cite{GuptaWRLGB12}%
.
For example, if a user can answer questions like
``who did you call last night?'' correctly, the authentication will succeed.
Using mobile or wearable devices for authentication will become more usable
in the future,
but users should have a fairly good long-term memory about their behaviors,
and that not easy for everybody.

@@

EpisoPass has been used by the authors for more than three years, and
the authors are using it for various services including
Twitter, Facebook, Amazon, Skype, etc.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, taking care of many passwords was really
a pain for the authors, but
currently all the information for generating passwords is put on the cloud
and no trouble has been found during the period.
%
After the introduction of browser extension,
logging into various services became even easier,
because visiting the EpisoPass service is unneccesary.

EpisoPass service have been on the Web and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}, but
unfortunately EpisoPass is currently not used by many people.
One big reason is that most people cannot fully understand the
idea of EpisoPass and also cannot fully trust it
because it is not operated by a big IT company.
% nor supported by famous computer users.
Another reason might be that users cannot estimate the strength
of EpisoPass.
Since all the questions and answers are
quite obvious to the users,
they might feel that everyone else also know the episode
and easily solve all the questions.
These kinds of psychological issues are quite important for
an authentication system for everybody,
and we hope to eliminate such obstacles in the future.

@@

\subsection*{Note.}

This paper is largely a translation of a 2013 paper published by the
author in Japanese\cite{WISS2013}. This is the first time that the
work is presented to an international audience in English.
Additionally, in the intervening three years the author has
developed the browser extension described in section \ref{extensionsection}.

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

\usepackage{url}
\urldef{\mailsa}\path|masui@pitecan.com|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Toshiyuki Masui%
\thanks{Thanks...}%
}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Faculty of Environment and Information Studies, Keio University\\
5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
\mailsa\\
\url{http://pitecan.com/}}

@@

Passwords have been used for various Web services and applications
for a long time, and currently the most popular authentication method on the Internet.
%
Since short passwords are easily guessed by attackers and
using the same password for different services is unsafe,
different long passwords should be used for different services.
However,
remembering many long passwords is almost impossible for ordinary humans.
%
According to a research in 2007,
people use 6.5 passwords on 25 Web services on average, and
4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.

Since passwords are difficult to handle,
various other authentication methods have been proposed.
For example,
image-based authentication\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}, 
biometrics authentication\footnote{
  % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
  \url{https://en.wikipedia.org/wiki/Biometrics}
},
behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, 
and many other authentication methods have been proposed.

@@

However,
password-based authentication is still the most
convenient and strong method\cite{Bonneau:ReplacePasswords},
and it is not supposed to become extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

If we have to live with password-based authentication systems,
we have to devise some ways to handle many passwords, and
various ``password managers'' have been proposed
\cite{OnePassword}%
\cite{Dashlane}%
\cite{MilPass}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}.
%
Password managers remember users' passwords and help them enter
passwords on various services.
%
Most password managers can manage various passwords by
asking users to remember a single ``master password'' to access the database.
%
Although password managers are useful,
users have to remember the master password
or use a special hardware device
for safely handling password managers, and
password managers usually run on limited devices.

@@

If we don't want to carry any special device for authentication,
all the information required for the authentication should be
kept in the brain.
%
However, the biggest problem of brain-based authentication is that
users cannot safely keep memories like long passwords or master password.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on users' episodic memories that they can never forget.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We propose a password manager \textit{EpisoPass} that generates strong passwords
based only on the user's secret episodic memories that the user cannot forget.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%
% Memories in human brain are not uniform.
We keep various memories in our brain, but different memories have different natures.
Some memories are very short-lived, and others are unforgettable.
When we have a very impressive experience,
that memory will stay in the brain for a long time and
cannot easily disappear.
On the other hand, when we study math and try to remember a new formula,
it is usually hard to memorize it unless we practice a lot,
since the knowledge about the formula is not related to
any personal experiences.
The former type of memory is called the episodic memory and
people cannot easily lose it.
Memories of passwords belong to the latter type and
people cannot easily remember them, just like people cannot
remember math formulas easily.

@@

The idea of using episodic memories for authentication has a long history.
Early papers suggested using episodic memories for creating passwords, and
authentication by using secret questions,
sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
has long been used as an
alternative to password-based authentication systems.
%
However, conversion from episodic memories to password strings
was not studied at all.

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a
candidate password string based on the selections.
When the user selects the right answers to all the questions,
the right password is calculated and shown at the top.

@@

@@

Questions and answers can be edited directly on the browser, and they can be
saved on the server by clicking the ``save to server'' button.
The Q-A data sets are saved on the server,
but no information about the correct answer or the
generated password is saved on the server.
The Q-A data in JSON format can be downloaded to the local machine
by cliking the ``save to file'' button.
the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.

@@

Character substitution is performed based on the hash value
calculated from concatinating all the selected answers.
%
For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
a hash value calculated from  ``\textbf{\texttt{Who's the bully:Ebisawa}}''
is used for the substitution.

@@

If a user doesn't like to use EpisoPass service on the Net,
he can use an EpisoPass application on Android
which does not use network connections.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
by clicking the ``Android app'' button at the top.
The application contains all the information required for generating passwords.
(The application is compiled and built on the server.)

@@

The calculation is performed on Android without network connection,
and the user can safely generate passwords 
without feeling the fear of being observed by attackers

\subsection{Using the browser extension}

@@

A browser extension is a JavaScript add-on program which runs
on top of existing HTML and JavaScript.
%
Figure \ref{extension} shows the login page of Amazon.com, with which
EpisoPass questions are automatically displayed by the browser extension.
%
Here, when the Amazon login page is accessed from the browser,
the browser extension program automatically runs on the page,
acquires questions and answers from the EpisoPass server,
and shows them to the user just the same way as the Android application.
%
After answering all the questions, a password is calculated from the
selected answers and pasted to the password input form of the page.
Using the extension, users can login to various services just by
answering questions, without seeing any password string.
It looks as if these services are offering
EpisoPass-based authentication.

@@

In the previous examples showing the author's real EpisoPass questions,
a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.
Such strings are used because they are easily memorable.
Of course any seed string can be used as seeds for various services,
and automatic generation of seed strings is possible,
although generating service specific unique seed string is not trivial.
For example, users can use the same username and password both
for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.

@@

It is difficult to provide enough number of fake answers to a question like
``what was your favorite sport?''
because possible answers are limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is easy.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', etc.
because we can use the list of states in the U.S.

In this way, fake answers can be easily generated
if it is possible to collect words which belong to the same
category as the right answer.
%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval tasks%
\cite{Huang:2012:LFC:2426725.2426728}% 
\cite{BooWa}% Boo!Wa!
\cite{Wang:2007:LSE:1441428.1442086}.% 
Using such systems, we can get a list of fake answers almost automatically.

@@

Although everyone has to use authentication systems on the Internet these days,
not all the people are good at handling passwords.
Even experienced computer users have trouble with passwords,
since choosing a good password is not intuitive and
people forget passwords very easily.
%
Using EpisoPass, people can use password-based systems without knowing
techniques for creating and remembering strong passwords.
They only have to provide
questions and answers based on secret episodic memories.
%
By integrating EpisoPass into existing password-based services,
people can even use services without noticing that passwords are
required for the service.
%
Our experience of using browser extensions suggests that
that approach is worth consideration.

@@

On many services, users are requested to change passwords periodically
to strengthen security.
%
Such a practice is not recommended these days
because humans cannot create strong passwords frequently\cite{Schneier:change}.
%
% A user can generate a new strong password by using a randam character generator
% on a password manager, but he might want to old passwords in case some trouble happens.
%
Using EpisoPass, users can just provide a date-related question
like the last question shown in Figure \ref{web1},
and generate different strong passwords based on the answer.
Using this technique, people can easily manage old and new passwords.

\subsection{Comparison with challenge-response authentication}

% 一方、{\SQ}を利用する認証の脆弱性を利用した攻撃が近年問題になっている。
% {\PW}を忘れたときのために、
% あらかじめ設定した{\SQ}に答えることによって{\PW}をリセットできるサービスがあり、
% 「母親の旧姓は?」や「最初に飼ったペットの名前は?」のような
% 質問に対してユーザが答を登録するようになっている。
% このような問題は他人が調べたり推測したりすることが容易であるうえに
% {\SQ}の数は一般的に少なく、
% {\PW}よりも脆弱だといえる\cite{Rabkin:2008:PKQ:1408664.1408667}。% 銀行20個調べて{\SQ}の弱さを指摘

In many services, users are adviced to define answers to secret questions like
``what is your mother's maiden name''
so that he can log into the service even when he forgets the password.
This kind of authentication is far less secure than simple password systems,
since it is fairly easy for attackers to know the right answer.
The variation of system-provided questions are usually small, and
such challenge-response systems are considered to be
insecure\cite{Rabkin:2008:PKQ:1408664.1408667}.

It would be better if the user can register his own secret questions
based on his episodic memory.
However, answers to user-generated challenge questions are more easily
forgotten or cracked,
and using simple challenge-responce is not considered to be safe enough
\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}.
%
Also, in this case,
the user should register the answer to the system in addition to the question.
Telling secret facts to service providers is like
registering raw password string on the server,
and it is not safe unless the strings are properly hashed and salted on the server.

%
%ユーザが作成した{\SQ}を使えばこのような問題はなくなるはずであるが、
%他人に解かれにくい問題をユーザが作成することは難しく、
%またユーザ自身が答を忘れてしまうことも多いと考えられている\cite{Just:2009:PCC:1572532.1572543}\cite{Schechter:2009:NSM:1607723.1608145}。
%
%また、古い記憶にもとづいて作成した秘密の問題は
%ユーザが想像するよりも解かれやすいという実験結果にもとづき、
%忘れない{\SQ}を複数利用する方法、
%問題と答を連想するために画像を利用する方法、
%複数の問題を連続的に利用する手法などが提案されている\cite{Renaud:2010:PQE:2146303.2146318}。

% {\EP}では、
% 他人には解くことが難しく自分では忘れないような{\SQ}を自由にいくつでも利用できるようになっている。
% 問題作成に慣れていないユーザには有効な{\SQ}を作成することは難しいかもしれないが、
% 次節で述べるように、適切な質問を選ぶことによりこの問題を解決できるはずである。

@@

To prevent such troble, it is safer to keep all the questions and answers
in a secret place or
use sufficient number of questions so that brute-force does not work.

@@

Old pictures can be used as the questions of EpisoPass,
just like the 5th question shown in Figure \ref{web1}.
Even when people cannot create good secret questions,
people can fairly easily select a secret image from their photo collections
and use it as the question.
For example, if you have an old picture of your friend,
you can use it as the question
and use his real name as well as other similar fake names.

@@

As shown in previous sections,
there have been many attemps for replacing password-based authentication systems,
but none of them are found to be better than
password-based systems\cite{Bonneau:ReplacePasswords}.
%
Although cognitive password systems have been studied for a
long time\cite{Lazar2011}\cite{Zviran:1990:UAC:100512.100538},
they were implemented as a replacement to password-based systems,
and no password-generation system have been proposed
based on cognitive authentication.

@@

The idea of using episodic memories for authtication is not new.
In fact, using episodic memories for selecting password
has generally been recommended,
and many current computer users are probably using password that are
in some way related to their episodic memories.

Recently, people are trying to use mobile devices for authentication,
because mobile devices remember all the user's behaviors and
the user can easily recall what he did%
\cite{Dandapat:2015:AYD:2702123.2702457}%
\cite{Das:2013:ECE:2493432.2493453}%
\cite{GuptaWRLGB12}%
.
For example, if a user can answer questions like
``who did you call last night?'' correctly, the authentication will succeed.
Using mobile or wearable devices for authentication works in many cases,
but users should have a fairly good long-term memory about their behaviors,
and that not easy for everybody.

@@

EpisoPass has been used by the authors for more than three years, and
the authors are using it for various services including
Twitter, Facebook, Amazon, Skype, etc.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, taking care of many passwords was really
a pain for the authors, but
currently all the information for generating passswords is put on the cloud
and no trouble has been found during the period.
%
After the introduction of browser extension,
logging into various services became even easier,
because visiting the EpisoPass service is unneccesary.

Unfortunately EpisoPass is currently not used by many people.
One big reason is that most people cannot fully understand the
idea of EpisoPass and also cannot fully trust it
because it is not operated by a big IT company nor supported by
famous computer users.
Another reason might be that users cannot estimate the strength
of EpisoPass.
Since all the questions and answers are
quite obvious to the users,
they might feel that everyone else also know the episode
and easily solve all the questions.
These kinds of psychological issues are quite important for
an authentication system for everybody,
and we hope to eliminate such obstacles in the future.

@@
